\documentclass[]{report}


% Title Page
\title{DATA COLLECTION CONCEPT}
\author{ KIZITO SEBUTEMBE EZEKIEL\\
	13/U/6970/PS\\
	213012200s
}

\begin{document}
\maketitle	{\Large \begin{center}
		MAKERERE UNIVERSITY\\
COLLEGE OF COMPUTING AND INFORMATION\\
TECHNOLOGY.\\
	\end{center}
\begin{center}
	 \textbf{\underline{ {\normalsize CHALLENGES OF LECTURE ROOMS, ATTENDANCE AND LEARNING AT CIT.} }}
\end{center}
\begin{flushleft}
	There have been a considerable number of literature emphasizing the role of facilitation brain development all the way up to upright reasoning and minds. Intelligence cannot just be attributed to genes but also the environment with which we are surrounded. In higher learning institutes such Makerere university, the learning environment plays a much significant role in the shaping of the minds of students that are yet to become upright elite citizens and face the undoubtedly steadfast growing economy.\linebreak
	
	In this case we are set to focus on the issues that could determine some of the challenges that come with our environment.(Thats to do with the lecture room capability, factors that affect attendance as we as the learning environment).\linebreak
	\begin{enumerate}
		\item •	Does the nature/design of the lecture rooms affect students behavior and response towards lectures?
		\item •	What are the new developments requirements students required by the design of the lecture rooms?
		\item •	How can the lecture rooms be designed better to enhance or boost student attendance and learning at CIT?
		\item •	Is there a moderate way between students and the lecture rooms design, learning environment as well as the nature of learning?
		\item •	How do the placements of tool use at CIT influence student behavior?
		\item •	How do students feel about the current lecture room and learning design at hand ?
		\item •	Is there a healthy platform to access study material from the lecturer’s end by the students?
		\item •	Are there incondusive environment situations amongst fellow students such as their accommodation, welfare,health etc?
	\end{enumerate}
	
	
\end{flushleft}
\end{document}

